SUPPLEMENTARY INFORMATION: Overlay databank unlocks data-driven analyses of biomolecules for all

### 2023-10-10 SI.tex
Updates from Overleaf

\documentclass[fleqn,10pt]{wlscirepSI}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage{xr}

@@

\begin{table}[p]
    \centering
    \begin{tabular}{l}
    Force field name and references \\
    \hline
    CHARMM36~\cite{klauda10}\\
    Slipids~\cite{jambeck12,jambeck12b,jambeck2012another,ermilova16,grote20}  \\
    MacRog~\cite{Kulig15b}  \\
    Amber Lipid14/17~\cite{dickson14,dickson22}  \\
    Charmm-Drude~\cite{li2017drude}      \\
    ECClipids~\cite{melcr18,melcr20,bacle21}  \\
    GROMOS-CKP~\cite{Chandrasekhar03,kukol09,piggot12}  \\
    Berger~\cite{berger97}  \\
    ECC-CHARMM36~\cite{nencini2019development}  \\
    Orange~\cite{catte16}  \\
    Poger~\cite{poger10}  \\
    GROMOS 43A1-S3~\cite{chiu09}  \\ 
    GAFFlipid~\cite{dickson12}  \\
    OPLS3e~\cite{roos19}  \\
    Ulmschneider~\cite{Ulmschneider09}  \\
    Chiu Gromos~\cite{chiu09}  \\
    AMOEBA~\cite{chu2018polarizable} \\
    \end{tabular}
    \caption{List of current force fields used in simulations in the Databank, with references.}
    \label{tab:ForceFields}
\end{table}

>>>>

\documentclass[fleqn,10pt]{wlscirepSI}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{graphicx}
\usepackage{tablefootnote}
\usepackage{xr}
\usepackage{comment}

@@

\begin{table}[p]
    \centering
    \begin{tabular}{l}
    Force field name and references \\
    \hline
    CHARMM36~\cite{klauda10}\\
    Slipids~\cite{jambeck12,jambeck12b,jambeck2012another,ermilova16,grote20}  \\
    MacRog~\cite{Kulig15b}  \\
    Amber Lipid14/17~\cite{dickson14,dickson22}  \\
    Charmm-Drude~\cite{li2017drude}      \\
    ECClipids~\cite{melcr18,melcr20,bacle21}  \\
    GROMOS-CKP~\cite{Chandrasekhar03,kukol09,piggot12}  \\
    Berger~\cite{berger97}  \\
    ECC-CHARMM36~\cite{nencini2019development}  \\
    Orange~\cite{catte16}  \\
    Poger~\cite{poger10}  \\
    GROMOS 43A1-S3~\cite{chiu09}  \\ 
    GAFFlipid~\cite{dickson12}  \\
    OPLS3e~\cite{roos19}  \\
    Ulmschneider~\cite{Ulmschneider09}  \\
    Chiu Gromos~\cite{chiu09}  \\
    AMOEBA~\cite{chu2018polarizable} \\
    OpenFF
    \end{tabular}
    \caption{List of current force fields used in simulations in the Databank, with references.}
    \label{tab:ForceFields}
\end{table}
